Contextual Identity: Freedom to be All Your Selves

### 2013-03-07 paper.tex
adverbs capitalized in title
minor cleanup

\title{Contextual Identity: Freedom to be all Your Selves}
%\title{Contextual Identity: All your selves are belong to you}

@@

\section{Summary}
People have multiple contextual identities, and often attempt to leverage them differently. Sharing personal information in
appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and seek to understand identity use better so we can develop tools for effective identity management.

>>>>

\title{Contextual Identity: Freedom to be All Your Selves}
%\title{Contextual Identity: All your selves are belong to you}

@@

\section{Summary}
People have multiple contextual identities for multiple different reasons. Sharing personal information in
appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and seek to understand identity use better so we can develop tools for effective identity management.
